merging_datasets

### 2020-04-22 merged data/merging_datasets.Rmd

```{r}
library(ggplot2)
library(dplyr)
```

```{r}
demographic<-read.csv("Demographic_Data.csv")
covid<-read.csv("states_current.csv")
stayhome<-read.csv("quarantine.csv")
google<-read.csv("Google_final.csv")
```

@@

covid<-covid%>%
  mutate(dateModified = as.Date(substr(dateModified,start = 0,stop = 10)),
         dateChecked = as.Date(substr(dateChecked,start = 0,stop = 10)))%>%
  select(-c(notes,hash))
colnames(covid)[1] <- "State"

@@

write.csv(all,"FullDataSet.csv")
```

>>>>

```{r}
library(ggplot2)
library(dplyr)
library(naniar)
```

```{r}
demographic<-read.csv("FINALDemographic_Data.csv")
covid<-read.csv("states_cases_data.csv")
stayhome<-read.csv("quarantine.csv")
google<-read.csv("Google_final.csv")
```

@@

colnames(covid)[2] <- "State"

@@

write.csv(all,"FullDataSet.csv")
names(all)
```
